On the Origin of Shrimpoluminescence

### 2022-01-08 sonoluminescence/paper/bak/v3/paper.tex
sdfadsfa

Studying SBSL, while offering advantages, also comes with complications. Due to the tiny volume of the bubble, directly measuring the temperature or pressure \emph{inside} the bubble is practically impossible \cite{suslick2008inside}. Still, the discovery of SBSL created a rush of effort to explain the phenomena with arguments ranging from the simplest models \footnote{There are far too many to try list here and we will not be interested in the vast majority of early models which are now irrelevant. References to these can be found in Gaitan \cite{gaitan1990experimental} and Brenner et al. \cite{brenner2002single}.} to more exotic explanations based of quantum field theory \cite{schwinger1993casimir,eberlein1996sonoluminescence,liberati2000sonoluminescence}. Over time, the \emph{phase-space} of SBSL has been refined: SBSL only occurs for a narrow range of driving pressures and for a particular combination of host-liquid and gas contnent in the bubble. The mapping of the phase-space of SBSL is a very rich subject and merits a review in itself (several exist \cite{brenner2002single,yasui2018acoustic}). We will not pursue this; our goal in this paper is to explain \emph{shrimpoluminescence} so we will mainly focus on SBSL as it occurs in \emph{water} containing \emph{air bubbles}, though occasionally we will comment on SBSL in other fluids.

The goal of this paper is to explain the basic ingredients needed to understand SBSL. While the author of this paper is particularly excited about shrimpoluminescence, this work will focus on SBSL in general as it is apparently simpler to create and characterize SBSL in the laboratory without involving shrimp (for example, convincing the shrimp to snap requires tickling them \cite{lohse2001snapping,versluis2000snapping,lohse2018bubble}). Besides notable exceptions \cite{tang2019bioinspired}, practically all work to study SL has not involved shrimp. Also absent will be any detailed discussion of MBSL. Instead, we will summarize the history of SBSL research up to now starting at the discovery of MBSL, leading to the subsequent discovery of SBSL and a rush of effort to explain it. We will then present a sketch of the relevant physics before visiting each topic in detail, finally combining everything together to give a complete picture of how shrimpoluminsence occurs.

@@

These very high estimates for the temperature in the bubbles led to a spark of interest more broadly: if the temerature in the bubble were really that large, then it should be possible for nuclear \emph{fusion} to occur \cite{}. An action movie featuring Keanu Reeves was even made with this at the center of the plot \footnote{It is called \emph{Chain Reaction} and I am unwilling to watch it.}. In the early 2000's, several papers were even published claiming that stable nuclear fusion was possible in the lab using a method based on SBSL \cite{}. Unfortunately these results turned out to be fraudulent \cite{}. Shortly after this fiasco, evidenced emerged that there are shape instabilities in the bubbles dynamics indicating that the converging shock-wave hypothesis is probably not right. This severely reduced the estimates for the temperature to $\sim 10,000$ K, ruling out the possibility of fusion occuring at all \cite{}. Moreover, it was shown that the light is most likely emitted from the \emph{bulk} of the bubble as opposed to its surface, making fits to a black body specturm (i.e. surface emission) incorrect \cite{}. Current estimates for the temperature at the center of a sonoluminescing bubble are $10,000-30,000$ K \cite{flannigan2005plasma,suslick2008inside,yasui2018acoustic,an2009diagnosing,an2008spectral,an2006mechanism}.

\subsection{Overview of Single-Bubble Sonoluminescence}

A sketch of SBSL is as follows: an air bubble is trapped at the center of an acoustically driven flask containing a fluid. The pressure wave in the fluid drives the expansion and contraction of a bubble and, in turn, the dyanmics of the gas in the bubble respond to the bubble's oscillations. The result is a very complicated, non-linear behavior that we will spend a good deal of this paper explaining. We will see that the dynamics of the gas \emph{inside} the bubble is nearly decoupled from the dyanmics of the \emph{fluid} containing the bubble so that we may look at these two problems seperately. What is now known is that the conditions required for a cavitating bubble to emit light depend sensitively on both the mechanical and chemical properties of the host-liquid and gas in the bubble, as well as the driving pressure and frequency \cite{brenner2002single,suslick2008inside}. The mechanical properties determine the pressure and temperature inside the bubble which in turn control chemical reactions: all of these data are used to explain the light emission. For extreme enough conditions in the bubble molecular dissociation, atomic/excited-state transitions, and electron-ion/electron-neutral atom bremsstrahlung all occur \cite{}. These are the processes which emit light \cite{}.

In very viscous fluids, such as 85\% aqueous H$_2$SO$_4$, the pressure and temperature are lower and most light emission occurs from molecular dissociation and ... \cite{}. In water, the pressure in the bubble is considerably higher and most light emission is due the electron-ion and electron-neutral atom bremsstrahlung \cite{}. Since our goal in this paper is to explain \emph{shrimpoluminescence}, which occurs in water, we will mainly focus on the later emission processes.

Firstly, we will look at the problem of the fluid containing the bubble; we will derive the equations of motion for the bubble's wall. Nextly, we will use our results for the bubble's wall to understand the dynamics of the gas trapped in the bubble. After that, we will combine these two and discuss solutions of the full problem. The ultimate result of this will turn out to be an estimate of the \emph{temperature} and \emph{pressure} in the bubble. We will then look at theories presenting the origin of light from the very hot contents of the bubble. Throughout the course of our journey, we will stick to the simplest results that still contain the essential physics we need. Connections to more advanced treatments, and thier implications, are provided for completeness.
\section{Bubble Dyanmics}
As it turns out, the dynamics of the bubble in SBSL (regardless of the light emission) are quite well described both qualitatively and \emph{quantitatively} by the classical theory of bubble dynamics \cite{prosperetti1999old,brenner2002single,prosperetti1986bubble,plesset1977bubble,suslick2008inside,yasui2018acoustic,brennen2014cavitation}. This isn't particularly surprising since the light emission and bubble collapse occur at different timescales (the duration of maximum compressions is $\sim 0.003\%$ of the bubble's period) \cite{suslick2008inside,prosperetti1999old,brenner2002single,prosperetti1986bubble,plesset1977bubble}. The starting point for any theory of the bubble dynamics is Rayleigh's original work \cite{rayleigh1917pressure}, now expounded upon by many others. The most widely known modern work is that of Plesset \cite{plesset1977bubble,plesset1949dynamics,prosperetti1986bubble}, resulting in the so called ``the Rayleigh-Plesset" (RP) equation. The derivation assumes the host liquid is incompressible, ultimately resulting in us neglecting the effects of sound radiated by the bubble. Corrections exist that improve upon the RP equation in various ways and we will discuss these below \cite{}. However, for brevity's sake, we will only derive the RP equation here and merely quote the others as they are very similar in form to the RP equation. The field of \emph{bubble dynamics} is quite mature and attempting to review it here would be out of scope of this paper; instead, the reader is referred to numerous books and reviews \cite{}.

@@

\section{The Bubble's Interior}

The theoretical progress on the bubble's interior since the discovery of SBSL in the late 1990's \cite{gaitan1992sonoluminescence} follows two paths \cite{brenner2002single,suslick2008inside,yasui2018acoustic}: (i) model calculations based on the RP equations and an equation of state for the pressure (from which we may calculate the temperature) are used to try to reproduce the easily measuremable dynamics of the bubble. (ii) We can model the light emission itself and compare our calculation to spectroscopic measurements of SBSL \cite{}. Obviously these are related topics, but the distinction in the context of SBSL is important as we will now see.

Most early progress on the bubble's interior depended on the former method: if we predict the right dynamics, then we might know the correct pressure and temperature in the bubble. These data are then used to try to describe the light emission \cite{}. This was preferred to studying the emitted spectra directly as careful measurements resulted in an almost featureless spectrum that could not be explained \cite{}. Calculating the dynamics of the bubble's wall from the RP equations (eq. \ref{eq:RP_2} or eq. \ref{eq:RP_3}) requires the pressure inside the bubble as input. We would like to find a suitable form for $\Delta p(t) \sim p_g(t)$ in the RP equations that reproduces the measured radius-time curve $R(t)$ for a stable cavitating bubble. It turns out that this is a very hard problem for a number of reasons: the conditions inside the bubble depend on gas diffusion and rectification (one-directional diffusion) between the liquid and the bubble, water-vapor conensation and evaporation inside the bubble, and chemical reactions between species in the bubble \cite{brenner2002single}. Brenner et. al elegantly summarized the impact of the problem \cite{brenner2002single}: ``one of the exciting features of modern research on SBSL is that it is a testing ground for how well mathematical models can deal with such a complicated situation"

Now let us breifly discuss the bubble's light spectrum. For the first decade or so, SBSL experiments were done using partially degased water as the liquid medium \cite{suslick2008inside,brenner2002single,gaitan1992sonoluminescence}. Careful measurements of the emission from SBSL in water resulted in an almost featureless spectrum \cite{}. Early attempts were made to fit this as black-body radiation resulting in \emph{huge} temperature estimates, e.g. $10^8$ K \cite{}. It was later discovered that SBSL is volume emission, indicating that black-body radiation is not valid \cite{}. Little progress was made on this front for quite some time \cite{brenner2002single}. The utility of analyzing the light spectrum of SBSL in water is succinctly described by Suslick \cite{suslick2008inside}: ``because of the inherent ambiguity associated with the analysis of featureless spectra of unknown origin, a more rigorous explanation is unlikely to be generated".

SBSL was first measured in partially degassed water \cite{gaitan1990experimental,gaitan1992sonoluminescence,brenner2002single} \footnote{Degassing lowers the ambient pressure, making it easier for bubbles to form.} Early attempts to understand the physics required exploring the phase-space over which SBSL occurs. Some attempts were made using non-aqueous host liquids e.g. alcohols, silicone oils \cite{weninger1995sonoluminescence,barber1997defining}, but experiments with air bubbles were not very sucessful \cite{barber1997defining}. Instead, different gases were tried in water. Recall, air is $\sim 80\%$ N$_2$, $\sim 20\%$ O$_2$, and $\sim 1\% $ Ar. Considering the relatively large content of O$_2$ and N$_2$, degassed water \emph{regassed} with N$_2$ or O$_2$ or a mixture were checked first and found not to produce SBSL \cite{hiller1994effect}. What was discovered was that a small amount of \emph{noble gas} was required for SBSL to occur \cite{barber1997defining,hiller1994effect,brenner2002single}. A result of this work was the \emph{argon rectification hypothesis} \cite{lohse1997sonoluminescing,brenner2002single,yasui2018acoustic,suslick2008inside}. The hypothesis claims that all species in the air inside the bubble besides argon are gradually ejected from bubble's interior until all that remains is pure argon. The theory is based on the fact that, at the elevated temperatures and pressures inside the bubble, dissociation of O$_2$ and N$_2$ into radicals is possible. These species then react with the water vapor radicals to form species that are soluble in the host fluid. As the pressure becomes very large during the compression stage of SBSL, the soluble materials leave the bubble and do not re-enter since thier solubility in water is enormous compared to the Ar content of the bubble \cite{lohse1997sonoluminescing}. Over many cycles, the contents of the bubble become nearly pure argon. Moreover, it was hypothesized that the SL would much more intense when the contents of the bubble are a pure inert gas: if the contents were e.g. molecules, bond breaking/formation would alter the pressure of the gas, ultimately reducing the temperature and reducing the amount of light production \cite{brenner2002single,yasui2018acoustic,lohse2018bubble,suslick2008inside}. This mechanism has been used to explain the relatively weak light, i.e. the low temperature, in MBSL: the bubbles are transient and cannot remove a significant amount of O$_2$ or N$_2$ over a single cycle. The current belief is that the contents of a bubble undergoing SBSL in water are pure argon after $\sim 10^3$ cycles \cite{brenner2002single,yasui2018acoustic}.

Most studies continued to use water as the host liquid until it was realized that SBSL in aqueous H$_2$SO$_4$ produces light $10^3$ times brighter than in water, allowing more precise measurments of the light spectum \cite{}. More importantly, new measurements revealed the phase space of SBSL in aqueous H$_2$SO$_4$ included a much larger range of pressures than water. Careful experiments revealed that the spectrum depended critically on the noble gas content and driving pressure. Suslick et. al measured the different emission spectra from Ar, Xe, and Kr bubbles in aqueous H$_2$SO$_4$ \cite{flannigan2005plasma,flannigan2006measurement,suslick2008inside}. Importantly, they were able to identify spectral lines from Ar$^+$, Xe$^+$, and Kr$^+$ excited state transitions, proving that the core of the bubble is plasma. Perhaps equally as crucially, they found the \emph{absence} of emission lines from components of aqueous H$_2$SO$_4$ vapor \cite{suslick2008inside,flannigan2006measurement,flannigan2006measurement}: the plasma contained only the noble gas, experimentally confirming the argon rectification hypothesis. Moreover, the spectra at different pressures were in very good agreement with detailed calcutions of emission from noble gas plasmas \cite{an2009diagnosing,an2008spectral}. Increased pressure results in increased collision rate between particles, broadening the excited state transition spectral lines \cite{an2008spectral,suslick2008inside,flannigan2005plasma,flannigan2006measurement}. Further calculations showed that the greatly increased viscosity and density of aqueous H$_2$SO$_4$, $\sim 10 \times$ and $\sim 1.3 \times$ larger than that that of water, lead to reduced (by orders of magnitude) pressure in the bubble at the same driving pressures \cite{an2009diagnosing}. The larger pressure in the bubbles in water was found to be consistent with the featureless emission spectrum \cite{suslick2008inside,yasui2018acoustic}.

@@

Let us now connect this to the problem of SBSL. In our case, we assume that our bubble has an \emph{ambient} radius $R_0$, leading to volume $V_0 =  4/3 \pi R_0^3$. Similarly, we will assume the pressure in the bubble at ambient radius $R_0$ is known and we will call it $p_0$. What we want to calculate is the pressure in the gas as a function of the bubble's radius $R(t)$ determined from the RP equations (eq. \ref{eq:RP_2} or eq. \ref{eq:RP_3}). Earlier we called the pressure in the gas $p_g(t)$ and we will stick with this here. Plugging these into eq. \ref{eq:P}, (and sneaking in a modification) we arrive at a very commonly used equation in the context of SBSL \cite{brenner2002single,lofstedt1995sonoluminescing,barber1997defining,lofstedt1993toward,hilgenfeldt1999simple}:
\begin{equation}
    p_g(t) = p_0 \left( \frac{R_0^3-h^3}{R^3(t)-h^3} \right)^ \Gamma
    \label{eq:p_g}
\end{equation}
The new variable $h$ that was added willy-nilly is called the \emph{Van der Walls hard-core radius} and its purpose is to make sure that, if the bubble collapses so strongly that its contents become incompressible (i.e. $R(t)\rightarrow h$), the pressure diverges \cite{lofstedt1993toward,brenner2002single}. Eq. \ref{eq:p_g} can be inserted into an RP equation which can then be integrated numerically to determine the bubble's dynamics. Now recall that one of main goals of modelling the bubble dynamics in SBSL was to calculate the temperature inside the bubble in order to model the light emission. Following similar steps to deriving $p_g(t)$, we can write down an equation for the temperature $T$ \cite{barber1997defining,brenner2002single}:
\begin{equation}
    T(t) = T_0 \left( \frac{R_0^3-h^3}{R^3(t)-h^3} \right)^ {\Gamma-1}.
    \label{eq:T(t)}
\end{equation}
Of course we still have to assign a reasonable guess to $T_0$, the temperature in the bubble at ambient radius $R_0$.

@@

\subsection{Experimental Results}

\begin{figure}
\includegraphics[width=0.9\linewidth]{figs/bubble_radius_1.pdf}
    \caption{\cite{barber1997defining,barber1992light}}
\label{fig:bubble_radius_1}
\end{figure}

Creating stable, single bubbles in a laboratory experiment is not particulary challenging and can be done with standard and low-cost materials \footnote{Actually, the phase-space for SBSL is ``small". The coordinates being driving amplitude, driving frequency, fluid composition, temperature, ambient pressure, gas content and composition, etc... What we are claiming is simple is the experimental setup once the correct parameters are identified.}. A typical experimental setup is shown in Fig. \ref{fig:flask}. Since we are mainly concerned with the light emission process itsself, we will only sketch the experimental setup; it can be summarized as follows \cite{lentz1995mie,gaitan1990experimental,gaitan1992sonoluminescence,gompf2000mie,brenner2002single,yasui2018acoustic,brennen2014cavitation,suslick2008inside}. A sample of degassed liquid is placed into a flask \footnote{Actually, the degassing part is quite important. We focus on it elsewhere.}. Coupled to the outside of the flask are piezoelectric transducers of some sort. The piezos are driven by a sinusoidal function generator to excite an acoustic resonance of the flask: a typical flask is a few cm across with a resonance at $\approx 20$ kHz \cite{brenner2002single}. The frequency is chosen to form a pressure \emph{antinode} at the center of the flask.

@@

Now that we know about how single, stable bubbles are formed in the lab, we can discuss two quantities of experimental quantities that have turned out the be the most important: (i) The bubble's radius may be measured by \emph{Mie scattering} and compared directly to solutions of the RP equations \cite{}. This can tell us about the temperature and pressure in the bubble. (ii) The other quantity of interest is the light spectrum which contains information on the bubble's contents: in principle, we can learn about temperature and pressure inside the bubble, with spectral lines telling us about the matter content \cite{}. As we will see, it is not simple to understand the light spectrum \cite{} and we will devote a section of this paper to this topic. For now, let us see what measurements of the bubble's dynamics have told us.

>>>>

Studying SBSL, while offering advantages, also comes with complications. Due to the tiny volume of the bubble, directly measuring the temperature or pressure \emph{inside} the bubble is practically impossible \cite{suslick2008inside}. Still, the discovery of SBSL created a rush of effort to explain the phenomena with arguments ranging from the simplest models \footnote{There are far too many to try list here and we will not be interested in the vast majority of early models which are now irrelevant. References to these can be found in Gaitan \cite{gaitan1990experimental} and Brenner et al. \cite{brenner2002single}.} to more exotic explanations based of quantum field theory \cite{schwinger1993casimir,eberlein1996sonoluminescence,liberati2000sonoluminescence}. Over time, the \emph{phase-space} of SBSL has been refined: SBSL only occurs for a narrow range of driving pressures and for a particular combination of host-liquid and gas content in the bubble. The mapping of the phase-space of SBSL is a very rich subject and merits a review in itself (several exist \cite{brenner2002single,yasui2018acoustic}). We will not pursue this; our goal in this paper is to explain \emph{shrimpoluminescence} so we will mainly focus on SBSL as it occurs in \emph{water} containing \emph{air bubbles}, though occasionally we will comment on SBSL in other fluids.

Let us now sketch the SBSL process a little more precisely. An air bubble is trapped at the center of an acoustically driven flask containing a fluid. The pressure wave in the fluid, shown as a function of time in Fig. \ref{fig:pulses}, drives the expansion and contraction of the bubble and, in turn, the dyanmics of the gas in the bubble responds to the bubble's oscillations. Within the phase-space relevant to SBSL, we get the very complicated non-linear response of the bubble's radius as shown in the figure. These dynamics lead to SBSL.

First, as the pressure decreases and becomes negative, the bubble expands gradually: surface tension and the negative pressure in the bubble tend to slow expansion. Eventually the pressure is increasing and. Once it becomes positive, the bubble violently collapses to its minimum radius: during compression, the negative pressure in the bubble is very large and works with the driving pressure to rapidly accelerate the bubble's wall. Since the collapse is so quick, the bubble's contents are adiabatically compressed, resulting in very large temperature and pressure in the bubble. If everything is just right, the temperature and pressure are large enough for a burst of light to produced as shown by the bottom curve in Fig. \ref{fig:pulses}. After the collapse, there is a period of \emph{after-bouncing} that continues until the pressure is negative again.

It turns out that the light pulse is very short: only $\sim0.003\%$ of the bubble's cycle \cite{suslick2008inside}, and its spectrum depends sensitively on both the mechanical and chemical properties of the host-liquid and gas in the bubble, as well as the driving pressure and frequency \cite{brenner2002single,suslick2008inside}. The mechanical properties determine the pressure and temperature inside the bubble which in turn control chemical reactions: all of these data are used to explain the light emission. For extreme enough conditions in the bubble, which occur only breifly, molecular dissociation and recombination, atomic/excited-state transitions, and electron-ion/electron-neutral atom bremsstrahlung are possible \cite{an2009diagnosing,an2008spectral,an2006mechanism,flannigan2005plasma,suslick2008inside,flannigan2006measurement}. These are now known to be the processes which emit light \cite{lohse2018bubble,yasui2018acoustic}.

Our goal in this paper is to present the bare minimum theory needed to understand \emph{shrimpoluminescence}. To keep things simple, we will concentrate on the dynamics of a bubble undergoing SBSL in the lab as it is apparently simpler to create and characterize SBSL without involving shrimp \footnote{ For example, convincing the shrimp to snap requires tickling them \cite{lohse2001snapping,versluis2000snapping,lohse2018bubble}. Besides notable exceptions \cite{tang2019bioinspired}, practically all work to study SL has not involved shrimp.}. Firstly, we will look at the problem of the fluid containing the bubble; we will derive the equations of motion for the bubble's wall. Nextly, we will use our results for the bubble's wall to understand the dynamics of the gas trapped in the bubble. The result of this will turn out to be an estimate of the \emph{temperature} and \emph{pressure} in the bubble. We will then look at theories presenting the origin of light from the very hot contents of the bubble. For relatively mild conditions inside the bubble, most light emission occurs from molecular dissociation processes \cite{}. These are the conditions in e.g. 85\% H$_2$SO$_4$. In water, the pressure in the bubble is considerably higher and most light emission is due the electron-ion and electron-neutral atom bremsstrahlung which occur at higher temperature \cite{}. Since we want to understand, shrimpoluminescence which occurs in water, we will mainly focus on the later processes. Moreover, throughout the course of our journey, we will stick to the simplest results that still contain the essential physics we need. Connections to more advanced treatments, and thier implications, are provided for completeness.

@@

These very high estimates for the temperature in the bubbles led to a spark of interest more broadly: if the temerature in the bubble were really that large, then it should be possible for nuclear \emph{fusion} to occur \cite{}. An action movie featuring Keanu Reeves was even made with this at the center of the plot \footnote{It is called \emph{Chain Reaction} and I am unwilling to watch it.}. In the early 2000's, several papers were even published claiming that stable nuclear fusion was possible in the lab using a method based on SBSL \cite{}. Unfortunately these results turned out to be fraudulent \cite{}. Shortly after this fiasco, evidenced emerged that there are shape instabilities in the bubbles dynamics indicating that the converging shock-wave hypothesis is probably not right. This severely reduced the estimates for the temperature to $\sim 10,000$ K, ruling out the possibility of fusion occuring at all \cite{}. Moreover, it was shown that the light is most likely emitted from the \emph{bulk} of the bubble as opposed to its surface, making fits to a black body specturm (i.e. surface emission) incorrect \cite{}. Current estimates for the temperature, which we will study in the rest of this paper, put the center of a sonoluminescing bubble at $10,000-30,000$ K \cite{flannigan2005plasma,suslick2008inside,yasui2018acoustic,an2009diagnosing,an2008spectral,an2006mechanism}.

\section{Bubble Dyanmics}
In this section, we will present the theory needed to model and understand the dynamics of a bubble undergoing SBSL. We will split this into parts. Firstly, we will derive the equations of motion for the bubble's wall. Nextly, we will review some important experimental developments that we will then use to argue for a simple model for the dynamics of the gas in the bubble. Lastly, we will compare results of a simulated bubble to experimental data. The connection to experiment will be what allows us to calculate the temperature in real bubbles.

\subsection{The Bubble Wall}
As it turns out, the dynamics of the bubble in SBSL (regardless of the light emission) are quite well described both qualitatively and \emph{quantitatively} by the classical theory of bubble dynamics \cite{prosperetti1999old,brenner2002single,prosperetti1986bubble,plesset1977bubble,suslick2008inside,yasui2018acoustic,brennen2014cavitation}. This isn't particularly surprising since the light emission and bubble collapse occur at different timescales (the duration of maximum compressions is $\sim 0.003\%$ of the bubble's period) \cite{suslick2008inside,prosperetti1999old,brenner2002single,prosperetti1986bubble,plesset1977bubble}. The starting point for any theory of the bubble dynamics is Rayleigh's original work \cite{rayleigh1917pressure}, now expounded upon by many others. The most widely known modern work is that of Plesset \cite{plesset1977bubble,plesset1949dynamics,prosperetti1986bubble}, resulting in the so called ``the Rayleigh-Plesset" (RP) equation. The derivation assumes the host liquid is incompressible, ultimately resulting in us neglecting the effects of sound radiated by the bubble. Corrections exist that improve upon the RP equation in various ways and we will discuss these below \cite{}. However, for brevity's sake, we will only derive the RP equation here and merely quote the others as they are very similar in form to the RP equation. The field of \emph{bubble dynamics} is quite mature and attempting to review it here would be out of scope of this paper; instead, the reader is referred to numerous books and reviews \cite{}.

@@

\subsection{The Bubble's Interior}
The theoretical progress on the bubble's interior since the discovery of SBSL in the late 1990's \cite{gaitan1992sonoluminescence} follows two paths \cite{brenner2002single,suslick2008inside,yasui2018acoustic}: (i) model calculations based on the RP equations and an equation of state for the pressure (from which we may calculate the temperature) are used to try to reproduce the easily measuremable dynamics of the bubble. (ii) We can model the light emission itself and compare our calculation to spectroscopic measurements of SBSL \cite{}. Obviously these are related topics, but the distinction in the context of SBSL is important as we will now see.

Most early progress on the bubble's interior depended on the former method: if we predict the right dynamics, then we might know the correct pressure and temperature in the bubble. These data are then used to try to describe the light emission \cite{}. This was preferred to studying the emitted spectra directly as careful measurements resulted in an almost featureless spectrum that could not be explained \cite{}. Calculating the dynamics of the bubble's wall from the RP equations (eq. \ref{eq:RP_2} or eq. \ref{eq:RP_3}) requires the pressure inside the bubble as input. We would like to find a suitable form for $\Delta p(t) \sim p_g(t)$ in the RP equations that reproduces the measured radius-time curve $R(t)$ for a stable cavitating bubble. It turns out that this is a very complicated problem: gas diffusion and rectification (one-directional diffusion) between the bubble and liquid vary the number of particles present and, to make things worse, the conditions inside the bubble facilitate chemical reactions between the air and water-vapor changing the properties of gas dynamically \cite{brenner2002single}. Brenner et. al elegantly summarized the significance of this problem \cite{brenner2002single}: ``one of the exciting features of modern research on SBSL is that it is a testing ground for how well mathematical models can deal with such a complicated situation"

The other method to understand the bubble's interior is its light spectrum. For the first decade or so, SBSL experiments were done using partially degassed\footnote{Degassing lowers the ambient pressure, making it easier for bubbles to form.} water as the liquid medium \cite{suslick2008inside,brenner2002single,gaitan1992sonoluminescence}. Careful measurements of the emission from SBSL in water resulted in an almost featureless spectrum \cite{}. Early attempts were made to fit this as black-body radiation resulting in \emph{huge} temperature estimates, e.g. $10^8$ K \cite{}. It was later discovered that SBSL is volume emission, indicating that black-body radiation is not valid \cite{}. Little progress was made on this front for quite some time \cite{brenner2002single}. The utility of analyzing the light spectrum of SBSL in water is succinctly described by Suslick \cite{suslick2008inside}: ``because of the inherent ambiguity associated with the analysis of featureless spectra of unknown origin, a more rigorous explanation is unlikely to be generated".

Some attempts were made to measure SBSL using non-aqueous host liquids e.g. alcohols, silicone oils \cite{weninger1995sonoluminescence,barber1997defining}, but experiments with air bubbles were not very sucessful \cite{barber1997defining}. Eventually, different gases were tried in water. Recall, air is $\sim 80\%$ N$_2$, $\sim 20\%$ O$_2$, and $\sim 1\% $ Ar. Considering the relatively large content of O$_2$ and N$_2$, degassed water \emph{regassed} with N$_2$ or O$_2$ or a mixture were checked first and found not to produce SBSL \cite{hiller1994effect}. What was discovered was that a small amount of \emph{noble gas} was required for SBSL to occur \cite{barber1997defining,hiller1994effect,brenner2002single}. A result of this work was the \emph{argon rectification hypothesis} \cite{lohse1997sonoluminescing,brenner2002single,yasui2018acoustic,suslick2008inside}. The hypothesis claims that all species in the air inside the bubble besides argon are gradually ejected from bubble's interior until all that remains is pure argon. The theory is based on the fact that, at the elevated temperatures and pressures inside the bubble, dissociation of O$_2$ and N$_2$ into radicals is possible. These species then react with the water vapor radicals to form species that are soluble in the host fluid. As the pressure becomes very large during the compression stage of SBSL, the soluble materials leave the bubble and do not re-enter since thier solubility in water is enormous compared to the Ar content of the bubble \cite{lohse1997sonoluminescing}. Over many cycles, the contents of an air bubble in water become nearly pure argon. Moreover, it was hypothesized that the SL would much more intense when the contents of the bubble are a pure inert gas: if the contents were e.g. molecules, bond breaking/formation would alter the pressure of the gas, ultimately reducing the temperature and reducing the amount of light production \cite{brenner2002single,yasui2018acoustic,lohse2018bubble,suslick2008inside}. This mechanism has been used to explain the relatively weak light, i.e. the low temperature, in MBSL: the bubbles are transient and cannot remove a significant amount of O$_2$ or N$_2$ over a single cycle. The current belief is that the contents of a bubble undergoing SBSL in water are pure argon after $\sim 10^3$ cycles \cite{brenner2002single,yasui2018acoustic}.

Still, most studies continued to use water as the host liquid until it was realized that SBSL in aqueous H$_2$SO$_4$ produces light $10^3$ times brighter than in water, allowing more precise measurments of the light spectum \cite{}. More importantly, new measurements revealed the phase space of SBSL in aqueous H$_2$SO$_4$ included a much larger range of pressure than water. Careful experiments revealed that the spectrum depended critically on the noble gas content and driving pressure. Suslick et. al measured the different emission spectra from Ar, Xe, and Kr bubbles in aqueous H$_2$SO$_4$, driven to have similar conditions to those in an air bubble in water \cite{flannigan2005plasma,flannigan2006measurement,suslick2008inside}. Importantly, they were able to identify spectral lines from Ar$^+$, Xe$^+$, and Kr$^+$ excited state transitions, proving that the core of the bubble is plasma. Perhaps equally as crucially, they found the \emph{absence} of emission lines from components of aqueous H$_2$SO$_4$ vapor \cite{suslick2008inside,flannigan2006measurement,flannigan2006measurement}: the plasma contained only the noble gas, experimentally confirming the argon rectification hypothesis. Moreover, the spectra at different pressures were in very good agreement with detailed calcutions of emission from noble gas plasmas \cite{an2009diagnosing,an2008spectral}. Increased pressure results in increased collision rate between particles, broadening the excited state transition spectral lines \cite{an2008spectral,suslick2008inside,flannigan2005plasma,flannigan2006measurement}. Further calculations showed that the greatly increased viscosity and density of aqueous H$_2$SO$_4$, $\sim 10 \times$ and $\sim 1.3 \times$ larger than that that of water, lead to reduced (by orders of magnitude) pressure in the bubble at the same driving pressures \cite{an2009diagnosing}. The larger pressure in the bubbles in water was found to be consistent with the featureless emission spectrum \cite{suslick2008inside,yasui2018acoustic}.

@@

Let us now connect this to the problem of SBSL. In our case, we assume that our bubble has an \emph{ambient} radius $R_0$ where the pressure is at its equilibrium value, $p_0$. The volume occupied by the gas is $V_0 =  4/3 \pi R_0^3$. We know that $p_0=p_\infty+2\sigma /R$ from earlier. What we want to calculate is the pressure in the gas as a function of the bubble's instantaneous radius $R(t)$ determined from the RP equations (eq. \ref{eq:RP_2} or eq. \ref{eq:RP_3}). Earlier we called the pressure in the gas $p_g(t)$ and we will stick with this here. Plugging these into eq. \ref{eq:P}, (and sneaking in a modification) we arrive at a very commonly used equation in the context of SBSL \cite{brenner2002single,lofstedt1995sonoluminescing,barber1997defining,lofstedt1993toward,hilgenfeldt1999simple}:
\begin{equation}
    p_g(t) = \left( p_\infty+2\frac{\sigma}{R_0} \right) \left[ \frac{R_0^3-h^3}{R^3(t)-h^3} \right] ^ \Gamma
    \label{eq:p_g}
\end{equation}
The new variable $h$ that was added willy-nilly is called the \emph{Van der Walls hard-core radius} and its purpose is to make sure that, if the bubble collapses so strongly that its contents become incompressible (i.e. $R(t)\rightarrow h$), the pressure diverges \cite{lofstedt1993toward,brenner2002single}. Eq. \ref{eq:p_g} can be inserted into an RP equation which can then be integrated numerically to determine the bubble's dynamics.

@@

Now recall that one of main goals of modelling the bubble dynamics in SBSL was to calculate the temperature inside the bubble in order to model the light emission. Following similar steps to deriving $p_g(t)$, we can write down an equation for the temperature $T$ \cite{barber1997defining,brenner2002single}:
\begin{equation}
    T(t) = T_0 \left( \frac{R_0^3-h^3}{R^3(t)-h^3} \right)^ {\Gamma-1}.
    \label{eq:T(t)}
\end{equation}
Earlier, we assumed that during the bubble's afterbounces and expansion, the gas dynamics were isothermal. Then we take $T_0$ to be the temperature of the liquid. The RP equation, eq. \ref{eq:RP_3}, combined with the gas dynamical equation, eq. \ref{eq:p_g}, and the known liquid and gas properties $\mu$, $\sigma$, and $h$, can be used to calculate the dynamics of an acoustically driven bubble, determining the time-dependence of the pressure and temperature in the bubble along the way.

\subsection{Bubbles in the Lab}
\begin{figure}
\includegraphics[width=0.9\linewidth]{figs/bubble_radius_1.pdf}
    \caption{\cite{barber1997defining,barber1992light}}
\label{fig:bubble_radius_1}
\end{figure}

Creating stable, single bubbles in a laboratory experiment is not particulary challenging and can be done with standard and low-cost materials \footnote{Actually, the phase-space for SBSL is ``small". The coordinates being driving amplitude, driving frequency, fluid composition, temperature, ambient pressure, gas content and composition, etc... What we are claiming is simple is the experimental setup once the correct parameters are identified.}. A typical experimental setup is shown in Fig. \ref{fig:flask}. Since we are mainly concerned with the explaining the light emission process itself, we will only sketch the experimental setup; it can be summarized as follows \cite{lentz1995mie,gaitan1990experimental,gaitan1992sonoluminescence,gompf2000mie,brenner2002single,yasui2018acoustic,brennen2014cavitation,suslick2008inside}. A sample of degassed liquid is placed into a flask \footnote{Actually, the degassing part is quite important. We focus on it elsewhere.}. Coupled to the outside of the flask are piezoelectric transducers of some sort. The piezos are driven by a sinusoidal function generator to excite an acoustic resonance of the flask: a typical flask is a few cm across with a resonance at $\approx 20$ kHz \cite{brenner2002single}. The frequency is chosen to form a pressure \emph{antinode} at the center of the flask.

@@

Now that we know about how single, stable bubbles are formed in the lab, we can discuss two experimentally accessible quantities that have turned out the be the most important: (i) The bubble's radius may be measured by \emph{Mie scattering} and compared directly to solutions of the RP equations \cite{}. This can tell us about the temperature and pressure in the bubble. (ii) The other quantity of interest is the light spectrum which contains information on the bubble's contents: in principle, we can learn about temperature and pressure inside the bubble, with spectral lines telling us about the matter content \cite{}. As we will see, it is not simple to understand the light spectrum \cite{} and we will devote a section of this paper to this topic. For now, let us see what measurements of the bubble's dynamics have told us.
